---
title: "Diapositivas"
author: "Fernando Franco M."
date: "27/9/2020"
output:
  beamer_presentation:
    theme: Copenhagen
  slidy_presentation: default
  ioslides_presentation: default
subtitle: Prueba de diapositivas
institute: Facultad de Ciencias Naturales y Matemáticas
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[skip=-2pt,belowskip=0pt]{caption}
- \captionsetup[table]{name=Tabla,position=above}
- \captionsetup[figure]{name=Figura,position=below}
- \BeforeBeginEnvironment{figure}{\vskip-8ex}
- \AfterEndEnvironment{figure}{\vskip+0ex}
- \titlegraphic{\includegraphics[width=7cm]{logo.png}} 

---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Slide with R Output

```{r cars, echo = TRUE}

library(knitr) 
library(kableExtra)
kbl(summary(cars),booktabs = TRUE, 
    caption ="Tabla de prueba")

```


## Slide with Plot
Se presenta el codigo usado para generar el grafico y el grafico $\rho$ 

```{r pressure,fig.cap="asas",fig.height=5}
plot(pressure)
```
